% ====================================================================
% POPW: Zero filler. Every section has ONE job.
% Target: ICHCIIS-26 Seoul, Oct 4, 2026
% ====================================================================
\documentclass[10pt,twocolumn]{article}
\usepackage[a4paper,margin=0.7in,columnsep=0.18in]{geometry}
\usepackage[T1]{fontenc}\usepackage[utf8]{inputenc}
\usepackage{microtype,booktabs,amsmath,graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[numbers,sort&compress]{natbib}
\graphicspath{{figures/}}
\newcommand{\popw}{POPW}
\newcommand{\need}[1]{\textcolor{red}{[#1]}}

\title{\popw: \$299 Multi-Task Assembly Verification with \\ Blockchain Micropayments \& IEEE 7005-2021 Governance}
\author{Bashara Aina}
\date{}

\begin{document}
\maketitle

% ABSTRACT — 3 numbers max.
\begin{abstract}
\need{1 sentence problem from your factory. 1 sentence \$299 system. 1 sentence pilot: N=?, opt-out=?, SUS=?. 150 words.}
\end{abstract}
\textbf{Keywords:} HCI; multi-task learning; assembly verification; consumer GPU; blockchain; IEEE 7005-2021

% ====================================================================
\section{Introduction}

\need{¶1: Describe YOUR factory. Not generic "manufacturing." Your dimsum line, your workers, one real quality dispute. This is the hook.}

\need{¶2: "We built \popw{} (\$299 GPU). It does 5 tasks. We tested it with N workers for X days. Results: [best 3 numbers]."}

% ====================================================================
\section{Related Work}

\need{¶1: Cite max 5 papers. "Existing systems cost \$10K+ and weren't tested with workers. Ours costs \$299 and was tested with N workers."}

\begin{table}[htbp]\centering\small\caption{\need{Fill from research.}}
\begin{tabular}{lcc}\toprule
\textbf{System} & \textbf{Cost} & \textbf{Tested with workers?}\\\midrule
YOLOv8m~\need{cite} & \$299 & No\\
ViMAT~\need{cite} & \$10K+ & No\\
IFAS~\need{cite} & \$15K+ & No\\
\popw{} & \$299 & \need{Yes — N workers}\\\bottomrule
\end{tabular}\end{table}

% ====================================================================
\section{Ethical Framework}

\need{Put 1–2 real worker quotes about being monitored. Not Foucault. Not Zuboff. Their actual words.}

% ====================================================================
\section{System}

\need{Figure 1: architecture diagram (draw.io, 30 min). Full width.}

\begin{table}[htbp]\centering\small\caption{Key specs.}
\begin{tabular}{lc}\toprule
\textbf{Metric} & \textbf{Value}\\\midrule
Parameters & \need{run model summary}\\
FPS on RTX 3060 & \need{run evaluate.py}\\
GFLOPs & \need{run evaluate.py}\\
Hardware cost & \$299\\\bottomrule
\end{tabular}\end{table}

% ====================================================================
\section{Results}

\need{Table 2: detection mAP, head pose MAE, activity Top-1. 3 rows.}
\need{Figure 2: confusion matrix — annotate "\% 1-bit-adjacent".}
\need{1 sentence: "This is fine-grained state discrimination, not detection failure."}
\need{\textbf{Ablation A}: single vs multi-task. Δ = \need{fill}. Took \need{Xh}.}
\need{\textbf{Ablation B}: FiLM on/off. Δ = \need{fill}. Took \need{Xh}.}

% ====================================================================
\section{Blockchain}

\need{1 mainnet transaction hash: \need{tx hash. 30 min work. \$2 gas.}}
\need{1 sentence: "Why blockchain? \need{honest answer from factory owner}"}
\need{Figure 3: cost bar chart. POPW \$799 vs \need{X} vs \need{X}.}

% ====================================================================
\section{Pilot at \need{Your Factory}}

\subsection{Setup}

\need{Figure 4: photo of worker at workstation with tablet visible. Blur face.}
\need{2 sentences: N=\need{X}, \need{X} days, \need{X}h shifts, tablet showed \need{what}.}

\subsection{Quantitative}

\begin{table}[htbp]\centering\small
\caption{This table wins or loses the paper.}
\begin{tabular}{lc}\toprule
\textbf{Measure} & \textbf{Result}\\\midrule
Opt-out rate & \need{X/Y}\\
SUS & \need{XX.X}\\
NASA-TLX pre$\to$post & \need{X$\to$X}\\
Trust (Jian scale) & \need{X.X/7}\\
Surveillance perception & \need{X.X/7}\\\bottomrule
\end{tabular}\end{table}

\subsection{Quotes}

\need{Quote 1 about earnings. Quote 2 about camera habituation. Quote 3 about something unexpected. This is what wins best paper.}

\subsection{Changes}

\need{1-2 things workers asked for that you implemented.}

\subsection{Limits}

\need{2 sentences. "2 weeks, 20 workers, food assembly, no control group."}

% ====================================================================
\section{Discussion}

\need{2 strongest findings. 1 future work direction. Code link. Done.}

% ====================================================================
\begin{thebibliography}{10}
\need{Cite 8-10 essential references only. Delete everything not directly cited.}
\end{thebibliography}
\end{document}
