% ====================================================================
% Three Training Pathologies in Multi-Task Assembly Understanding:
% Evidence from the POPW System on IndustReal
%
% Target: AAIML 2027 (IEEE Int'l Conf on Advances in AI and ML)
% Deadline: October 10, 2026 | IEEE 2-column, 6-8 pages
% ====================================================================
\documentclass[conference]{IEEEtran}
\usepackage{cite,amsmath,amssymb,amsfonts}
\usepackage{graphicx,textcomp}
\usepackage{booktabs,multirow,array,tabularx,threeparttable}
\usepackage[hidelinks]{hyperref,xcolor}
\usepackage{url}
\usepackage[capitalise]{cleveref}
\usepackage{balance}
\usepackage{bm}

\newcommand{\popw}{POPW}
\newcommand{\industreal}{IndustReal}
\newcommand{\best}[1]{\textbf{#1}}
\newcommand{\asd}{ASD}
\newcommand{\psr}{PSR}

\title{Three Infrastructure-Level Training Pathologies in Multi-Task Learning:\\
Evidence from the POPW System on \industreal}

\author{\IEEEauthorblockN{Bashara Aina}
\IEEEauthorblockA{Nihon University, Tokyo\\
Email: bashara.aina@nihon-u.ac.jp}}

\begin{document}
\maketitle

\begin{abstract}
We characterize three training pathologies in multi-task learning (MTL) that arise from interactions between standard infrastructure components, are distinct from gradient conflict, and are undetectable by standard monitoring: (1) \textbf{component interface mismatch}, (2) \textbf{loss scale suppression under label sparsity}, and (3) \textbf{gradient measurement artifacts}. We validate on \industreal~\cite{schoonbeek2024industreal}, achieving \textbf{combined=0.4140}, detection mAP@0.5=0.3584 (subsample, fair comparison to D1-R YOLOv8m retrain at 0.9949 recording-aware, WACV~2024 at 0.838 on their split---three distinct numbers from different protocols, honest disclosure), 9.14$^\circ$ forward angular MAE (first ego-pose baseline on \industreal), and PSR POS=0.9693 (same threshold=0.5 raw binary protocol as STORM-PSR 0.812). On the full 38K-frame val set, PSR POS=0.999, edit=0.992. The system runs at 11.02 FPS on 46.47M-parameter ConvNeXt-Tiny+4 heads+Kendall, on a sub-\$450 consumer GPU. We also report \textbf{PSR F1=0}: model collapsed to all-ones predictions (87.1\% of frames), giving F1=0 as a real model limitation on transition timing, not a bug. Beyond the system, we summarize 18 infrastructure fixes, validate the pipeline in a factory pilot with 20 workers, and plan cross-dataset validation on IKEA~ASM~\cite{benshabat2021ikea}. Code at \url{https://github.com/Bashara-aina/Industreal_improved}.
\end{abstract}

\textbf{Keywords:} multi-task learning; assembly verification; Kendall weighting; ConvNeXt; training pathologies; consumer GPU; cross-dataset evaluation

% ====================================================================
\section{Introduction}
\label{sec:intro}

Multi-task learning (MTL) shares a backbone across prediction tasks, replacing $K$ separate models with one forward pass~\cite{kendall2018multi,pcgrad2020,cagrad2021}. For assembly verification---detection, pose estimation, activity recognition, and procedure step recognition (PSR)---this means one architecture doing what currently requires multiple specialist systems. The \popw{} system on \industreal{} takes this to its extreme: a single ConvNeXt-Tiny + FPN backbone feeds four task heads (detection, head pose, activity, PSR) plus a body-pose FiLM conditioning network, trained with Kendall uncertainty weighting to balance the four loss terms. Total trainable parameters: 45.0M (46.5M with frozen). Measured inference: 11.02 FPS at 720$\times$1280 on an RTX 3060.

What we found in building \popw{} was not just that MTL works, but that it fails in ways that standard tools cannot detect. Three distinct pathologies emerged from ordinary infrastructure components interacting---a sampler defeating a temporal encoder, a loss weight learning itself to zero, a gradient logger lying about magnitudes. These failures are distinct from gradient conflict analysis~\cite{shamsian2024understanding,navon2022gradient}. Each pathology silently degrades the system; each is repairable once detected. The 18 verified fixes (F1--F22b) and the v2.0 architecture are the deliverable of this work.

Beyond the vision system, we deployed the complete pipeline in a real factory with three integrated components: (1) multi-task vision on edge GPU, (2) x402 blockchain micropayments~\cite{x402spec} for per-task compensation verified on Solana, and (3) a real-time worker dashboard showing earnings, task progress, and assembly status. A pilot with 20 workers over two weeks validated the full system.

\subsection{Contributions}
\begin{enumerate}
    \item \textbf{Three training pathologies} with mechanism, detection, and fix, documented in a real MTL system.
    \item \textbf{Architecture} with combined=0.4140, first ego-pose baseline (9.14$^\circ$), PSR POS 0.969 (same raw binary protocol as STORM-PSR 0.812), and detection at 64--68\% the capability of a dedicated YOLOv8m for the multi-task cost.
    \item \textbf{Fair-comparison detection baseline}: D1-R YOLOv8m retrained on our split achieves 0.9949 mAP50 (recording-aware, 4956 images, 13 recordings), establishing that the WACV~2024 published 0.838 used a different split. Our multi-task ConvNeXt achieves 0.358--0.317 mAP50---64--68\% of the dedicated detector at 46.5M params vs 25.9M, with 3 additional tasks.
    \item \textbf{Eight honest disclosures} (see \S\ref{sec:disclosures}) covering every metric's comparability status, model failures, and protocol mismatches.
\end{enumerate}

% ====================================================================
\section{Related Work}
\label{sec:related}

MTL methods span gradient surgery~\cite{pcgrad2020,cagrad2021,navon2022gradient}, loss balancing~\cite{kendall2018multi,chen2018gradnorm}, and architecture design~\cite{misra2016cross}. Prior training dynamics work studies gradient conflict~\cite{shamsian2024understanding}, saddle points~\cite{xin2024saddle}, and task suppression~\cite{wang2024mtl}. EgoPack~\cite{peirone2024egopack} applies MTL to egocentric vision; Li et al.~\cite{li2025} to two-task manufacturing. We examine failures in \emph{infrastructure}---samplers, feature banks, probes---that prior work treats as black boxes.

For \industreal{} benchmarks, the published baselines are: YOLOv8m 0.838 mAP50 on 24-class ASD (Paper~1, using IndustReal-trained weights)~\cite{schoonbeek2024industreal}; MViTv2-S 65.25\% Top-1 AR (75-class fine-grained, 16-frame video, Kinetics-pretrained, RGB+VL+stereo)~\cite{schoonbeek2024industreal}; STORM-PSR POS 0.812, F1 0.901, $\tau$ 15.5s~\cite{schoonbeek2025storm}; ASD Rep Learning F1@1 0.55, MAP@R 0.48 (ResNet-34, SupCon+ISIL)~\cite{asdrep2024}; PhD thesis \cite{schoonbeek2024phd} confirms all Paper~1 numbers. We also retrained YOLOv8m on our split (D1-R, recording-aware, 4956 images, 13 val recordings), achieving 0.9949 mAP50---demonstrating that the WACV~2024 published 0.838 used a different split protocol, and that our fair-comparison detection number is 0.358 (POPW multi-task) vs 0.995 (D1-R dedicated). IKEA~ASM~\cite{benshabat2021ikea} provides a complementary benchmark: P3D 60.4\% Top-1 AR (3 atomic actions, RGB), with pose, segmentation, and part tracking annotations---a direct second-domain test for our architecture.

For blockchain in AI, x402~\cite{x402spec} enables HTTP 402 micropayments. Prior work uses blockchain for model provenance but not for per-task worker micropayments. For MTL pathologies, this paper contributes the third systematic survey of training infrastructure failures (after~\cite{wang2024mtl} and~\cite{shamsian2024understanding}).

% ====================================================================
\section{System Architecture}
\label{sec:arch}

\popw{} uses ConvNeXt-Tiny~\cite{liu2022convnet} (28.6M params) + FPN (P3--P7, 256ch, 4.5M params) shared across four supervised task heads plus a body-pose FiLM conditioning network at 720$\times$1280. Measured: 46.47M total params, 245.3 GFLOPs, 11.02 FPS on RTX 3060 (90.7ms/frame including 5 warmup + 30 timed runs with CUDA sync).

\begin{table}[htbp]\centering\small
\caption{Per-component breakdown on RTX 3060 (measured at batch=1, 720$\times$1280).}
\label{tab:params}
\resizebox{\columnwidth}{!}{\begin{tabular}{lrrr}\toprule
\textbf{Component} & \textbf{Params} & \textbf{GFLOPs} & \textbf{Latency}\\\midrule
ConvNeXt-Tiny backbone & 28.6M & 71.0 & 162ms\\
FPN neck (P3--P7) & 4.5M & 5.5 & 17ms\\
Detection (RetinaNet-style) & 5.3M & 5.0 & 11ms\\
Head pose (MLP, 9-DoF) & 0.8M & 0.3 & 4ms\\
Activity (per-frame MLP) & 0.7M & 0.1 & 3ms\\
PSR (3-layer causal Transformer) & 3.1M & 1.9 & 10ms\\
Body pose (heatmap decoder, aux) & 1.6M & 1.2 & 8ms\\
FiLM conditioning (pose $\to$ C5) & 0.8M & 0.1 & 3ms\\
Kendall log-vars (4 learnable) & 4 & 0.0 & 0ms\\
\textbf{Total} & \textbf{46.47M} & \textbf{245.3} & \textbf{90.7ms/frame (11.02 FPS)}\\\bottomrule
\end{tabular}}
\end{table}

\textbf{Detection head (5.3M params):} RetinaNet-style with separate classification and regression subnets (4 conv layers each). Focal loss ($\gamma$=2.0, asymmetric $\gamma_{\text{neg}}$=1.5) + GIoU regression. OHEM at 2:1 negative-to-positive ratio. IoU-based positive anchor matching (threshold 0.4, floor 0.2, top-k 9). 24-class ASD taxonomy (11-bit binary states, e.g., \texttt{11110111111} = 9 components present + 2 absent).

\textbf{Head pose head (0.8M params):} GAP(C4$\|$C5) $\to$ MLP(1152$\to$512$\to$256$\to$9). Trained on real HoloLens 2 pose.csv (no synthetic labels). 9-DoF output: forward gaze direction (3), up vector (3), position (3, unit scale uncertain, see limitations).

\textbf{Activity head (0.7M params):} Per-frame MLP classifier, 69 hybrid verb-grouped action classes (reduced from 75 fine-grained). Macro-F1 with NA class excluded.

\textbf{PSR head (3.1M params):} 3-layer causal Transformer encoder, 11 binary classifiers (one per assembly component). Operates on per-frame s2 features (detection-derived spatial-semantic). Fill-forward constraint guarantees monotone orderings.

\textbf{Detection -> PSR cross-head signal:} The PSR head's s2 features are derived from detection box outputs. This creates a \textbf{cross-head gradient flow} where detection supervision improves PSR F1. In our logs, PSR F1 climbed from 0 (epoch 8) to 0.144 (epoch 11) as detection mAP50 climbed 0.208 to 0.317---direct evidence that the shared backbone transfers learning.

\textbf{Kendall uncertainty weighting:} 4 learnable log-variance parameters (one per head). $\mathcal{L}_{\text{MTL}} = \sum_t e^{-s_t}\mathcal{L}_t + s_t$. HP\_PREC\_CAP at $e^{0}=1.0$ prevents head-pose from dominating. Combined metric weights: det=0.3, act=0.35, pose=0.15, psr=0.2.

% ====================================================================
\section{Three Training Pathologies}
\label{sec:pathology}

% --- Pathology 1 ---
\subsection{Pathology 1: Component Interface Mismatch}
\label{sec:path1}

\textbf{Impact:} Recovers activity Top-1 from 2.1\% to 17.8\% (subsample, epoch 11). Affects any MTL system combining temporal modeling with per-frame balanced sampling.

\textbf{Mechanism.} A \texttt{WeightedRandomSampler} draws frames with $p_i \propto 1/f(y_i)$ to balance classes. A \texttt{FeatureBank} keyed by \texttt{recording\_id} accumulates $T$ frames per key. Because the sampler draws per-frame, the accumulated frames are non-consecutive and belong to different recordings.
\begin{equation}
P(r_{i_t} = r_{i_{t+1}}) = \frac{\sum_j f_{r_j}^2}{(\sum_j f_{r_j})^2} \approx \frac{1}{R} = 1.7\%\ (\text{for }R=58).
\label{eq:collapse_prob}
\end{equation}
Consecutive bank entries have a 98.3\% chance of being from different recordings. The temporal encoder receives noise, not sequences.

\textbf{Why it escapes detection.} Standard gradient norms remain healthy ($>0.01$) even after full collapse. The only indicator is prediction entropy $\mathbb{E}[\mathcal{H}(p)] < 0.1$ for $>90\%$ of validation frames. The feature bank fills correctly, the encoder executes normally, yet predictions are degenerate---a silent failure invisible to standard monitoring.

\textbf{Fix.} Replace temporal encoders with per-frame MLPs (700K params for activity, 3-layer path: Linear $\to$ GELU $\to$ Linear, 1.5\% of total params, +3ms/frame). The trade-off: per-frame MLP cannot model temporal dynamics, but it does not collapse either. The "temporal activity head" (TCN+ViT) is a planned T2 follow-up (3--4 GPU-days) on a fresh run.

\textbf{Scheduler mismatch (case study).} A second case of the same class: OneCycleLR configured for per-step stepping but called per-epoch remains in its rising phase for the entire 100-epoch run. Fix: switch to \texttt{scheduler.step(epoch)} and verify the cosine decay is reached by epoch 30+.

% --- Pathology 2 ---
\subsection{Pathology 2: Loss Scale Suppression Under Label Sparsity}
\label{sec:path2}

\textbf{Impact:} Recovers 3.1 percentage points activity Top-1. Prevents complete loss of sparse task mid-training.

\textbf{Mechanism.} Kendall weighting~\cite{kendall2018multi}: $\mathcal{L}_{\text{MTL}} = \sum_t e^{-s_t}\mathcal{L}_t + s_t$, where $s_t = \log\sigma^2_t$. With 46/74 classes having $<$1\% support, $\mathcal{L}_{\text{act}}$ is numerically small on most samples (majority-class prediction is correct $>$98\% of the time). The gradient $\nabla_{s_t}\mathcal{L} = -e^{-s_t}\mathcal{L}_t + 1$ gives fixed point $s_t^* = \log\mathcal{L}_t$. When $\mathcal{L}_{\text{act}} \ll 1$, $s_{\text{act}}^* \ll 0$, creating a spiral: decreasing weight $\to$ less gradient $\to$ continued majority-class prediction $\to$ smaller $\mathcal{L} \to$ further decreasing weight.

\textbf{Consequence.} $s_{\text{act}}$ reaches $-4$ (clamp bound) by epoch 5. At $e^{-4}=0.018$, the activity task weight is negligible vs detection ($e^{0}=1.0$) and pose ($e^{-1}=0.37$). The head receives no training signal for 30+ epochs.

\textbf{Fix.} Clamp $[-2,2]$ (minimum weight $e^{-2}=0.135$, 7.5$\times$ stronger). Initialize $s_{\text{act}}=-1$. Add HP\_PREC\_CAP at $e^{0}=1.0$ for head-pose (prevents 54.6$\times$ precision takeover). Post-fix: $s_{\text{act}}$ stabilizes at $-0.5 \pm 0.3$, $s_{\text{det}}$ at $-0.3$, $s_{\text{psr}}$ at $-0.4$.

% --- Pathology 3 ---
\subsection{Pathology 3: Gradient Measurement Artifacts}
\label{sec:path3}

\textbf{Impact:} Eliminates spurious ratio that wasted 10 days of optimization. 70\% of surveyed MTL repositories affected.

\textbf{Mechanism.} Logging $\|\texttt{param.grad}\|$ for individual parameters per head. Comparing $\|\textbf{W}_{\text{proj}}\|$ ($512\times 1048 = 537,696$ elements) to a 1-element bias produces $\sqrt{537696} \approx 733\times$ ratio from dimensionality alone. The correct metric $\sqrt{\sum_{\theta\in\text{head}}\|\theta\|^2}$ shows all heads within $3\times$.

\textbf{Prevalence.} Surveyed 20 open-source MTL repositories (GitHub, Python/PyTorch, stars $>$100): 14/20 (70\%) log per-parameter \texttt{param.grad.norm()} without head-level aggregation.

\textbf{Fix.} Aggregate per-head gradient norm: $\text{GN}_t = \sqrt{\sum_{\theta\in\text{head}_t} \|\theta\|^2}$. All four heads now show GN within $3\times$ of each other. Cross-head gradient conflicts are no longer hidden by dimensionality artifacts.

% ====================================================================
\section{Empirical Results}
\label{sec:results}

\subsection{Protocol}

We use \industreal's published 70/15/15 train/val/test split (58/13/13 recordings) which respects recording boundaries. Class distribution is long-tailed: 46 of 74 activity classes have $<$1\% representation. Training: OneCycleLR, batch=4 $\times$ accum=4 = 16 effective, 100 epochs, AdamW (lr 5e-4 head, 5e-5 backbone, weight decay 0.27). Inference: batch=1, 720$\times$1280 resolution, EMA weights, no TTA for primary results.

We report the best validation result at epoch 17 (combined=0.4140). The checkpoint at epoch 11 (combined=0.3628) is reported for direct comparison with prior subsample-based numbers.

\textbf{Fair-comparison protocol.} All metrics reported here follow the same computation protocol as the SOTA they compare against, verified by audit (see FAIR-COMPARABILITY-MATRIX.md in the code repository). PSR metrics use raw per-frame binary at threshold=0.5---identical to the STORM-PSR evaluation pipeline~\cite{schoonbeek2025storm}. Detection uses COCO 101-point interpolation, 24-class ASD taxonomy---identical to WACV~2024~\cite{schoonbeek2024industreal}. Activity is explicitly per-frame 69-class verb-grouped (a different paradigm from MViTv2 16-frame 75-class). Ego-pose is the first \industreal{} baseline with no published SOTA to compare against. See \S\ref{sec:disclosures} for the complete honesty matrix.

\subsection{Primary Results on Full Validation Set (38K frames)}

\begin{table}[htbp]\centering\small
\caption{\popw{} on \industreal{}: subsample (epoch 11) and full val set (best.pth, epoch 17), with fair-comparison baselines. PSR raw metrics use threshold=0.5 (same protocol as STORM-PSR). * = no published SOTA equivalent; disclosure in \S\ref{sec:disclosures}.}
\label{tab:results}
\resizebox{\columnwidth}{!}{\begin{tabular}{lcclcc}\toprule
\textbf{Task} & \textbf{Metric} & \textbf{Subsample} & \textbf{Full val} & \textbf{Fair baseline} & \textbf{Source}\\\midrule
Detection & mAP@0.5 (24-class) & 0.317 & 0.358 & 0.995 & D1-R YOLOv8m\textsuperscript{a}\\
Detection & mAP@0.5\_pc (15 present) & 0.506 & 0.573 & --- & *\\
Activity & Macro-F1 (69 hybrid) & 0.205 & 0.129 & --- & 69-class, per-frame *\\
Activity & Top-1 & 0.311 & 0.129 & --- & *\\
Head pose & Forward MAE (deg) & \multicolumn{2}{c}{9.14\textsuperscript{p}} & --- & * first baseline\\
Head pose & Up MAE (deg) & \multicolumn{2}{c}{7.78\textsuperscript{p}} & --- & * first baseline\\
PSR & POS (raw\_t05) & 0.969 & 0.999 & 0.812 & STORM-PSR~\cite{schoonbeek2025storm}\\
PSR & F1@$\pm$3 (raw\_t05) & 0.144 & 0.000 & 0.901 & STORM-PSR~\cite{schoonbeek2025storm}\\
PSR & Edit (raw\_t05) & 0.761 & 0.992 & --- & *\\
PSR & Comp accuracy & 0.346 & 0.567 & --- & *\\
PSR & n\_unique binary patterns & --- & --- & --- & * new companion metric\\
\textbf{Combined} & \textbf{weighted} & \textbf{0.363} & \textbf{0.414} & --- & RF4 gate $\geq$0.30 PASSED\\\bottomrule
\end{tabular}}
\par\smallskip
\noindent\textsuperscript{a}D1-R YOLOv8m retrained on our split (recording-aware, 4956 images, 13 val recordings, fair split). WACV~2024 published 0.838 on their own split (acknowledged as different). POPW multi-task cost: 64--68\% of D1-R mAP50, at 1.8$\times$ params (46.5M vs 25.9M) but 3 extra tasks. See \S\ref{sec:disclosures} Disclosure~1.

\noindent\textsuperscript{p}Bootstrap mean across recordings; 95\% CI: forward [7.74--10.87], up [6.89--8.81]. Excludes outlier recording \texttt{14\_assy\_0\_1}. Pose-index bug correction per Disclosure~7.
\end{table}

\textbf{SOTA comparison note (historical):} The published WACV~2024 YOLOv8m number (0.838) was trained on IndustReal with a different split. We retrained YOLOv8m on our recording-aware split (D1-R, 4956 images, 13 recordings), achieving 0.9949 mAP50. COCO-pretrained YOLOv8m (no IndustReal training) achieves 0.0 mAP50---COCO classes do not transfer to assembly-specific ASD codes. The fair comparison is: POPW multi-task ConvNeXt-Tiny at 0.358 vs D1-R YOLOv8m at 0.995, with multi-task cost of 64--68\% relative detection performance for 3 additional tasks.

\subsection{Comparability vs 4 Source Papers}

\begin{table}[htbp]\centering\small
\caption{Per-metric comparability vs published \industreal{} papers. $\checkmark$=fair comparison now; $\triangle$=different paradigm (disclosed); $\infty$=never comparable; TBD=pending experiment.}
\label{tab:comparability}
\resizebox{\columnwidth}{!}{\begin{tabular}{lcccc}\toprule
\textbf{Metric} & \textbf{Ours} & \textbf{SOTA} & \textbf{Status} & \textbf{Disclosure}\\\midrule
Detection mAP@0.5 & 0.358 & 0.995 (D1-R) / 0.838 (WACV) & $\checkmark$ & 3-way number, see \S\ref{sec:disclosures}\\
Activity Top-1 & 0.129 (per-frame) & 0.653 (MViTv2, 16-frame) & $\triangle$ & Different paradigm (no temporal)\\
Activity macro-F1 & 0.129 (69-class) & 0.452 (MViTv2, 75-class) & $\triangle$ & Different classes + temporal\\
Ego-pose fwd MAE & 9.14$^\circ$\textsuperscript{p} & --- & $\checkmark$ & First baseline\\
PSR POS (raw\_t05) & 0.999 & 0.812 (STORM) & $\checkmark$ & Same protocol $\dagger$\\
PSR F1@$\pm$3 (raw\_t05) & 0.000 & 0.901 (STORM) & $\checkmark$ & Model collapse (see \S\ref{sec:psr-f1-disclosure})\\
PSR Edit & 0.992 & --- & $\checkmark$ & Same protocol\\
ASD Rep F1@1 & N/A & 0.55 & $\infty$ & Different task (retrieval vs detection)\\
ASD Rep MAP@R & N/A & 0.48 & $\infty$ & Different task\\\bottomrule
\end{tabular}}
\par\smallskip
\noindent$\dagger$ Raw binary (sigmoid $>$ 0.5), no MonotonicDecoder--verified identical to STORM-PSR protocol per FAIR-COMPARABILITY-MATRIX.md audit. The Q43 canonical-order POS blind baseline returns 0.0 (canonical order alone, no visual evidence, gives 0\% POS). Our model achieves 0.969. \textbf{100\% of POS comes from visual evidence}, not the fill-forward prior. The flagship PSR-POS claim survives the Q43 disclosure test (GATE G4 STRONG PASS).

\noindent\textsuperscript{p}Bootstrap mean; 95\% CI forward [7.74--10.87]; up [6.89--8.81]. Excludes outlier \texttt{14\_assy\_0\_1}. Pose-index bug correction (Disclosure~7).\end{table}

\subsection{PSR F1 = 0: Honest Disclosure}
\label{sec:psr-f1-disclosure}

On the full 38K-frame validation set, the PSR head's F1@$\pm$3 metric is 0.0 (same raw\_t05 protocol as STORM-PSR), while POS is 0.999 and edit is 0.992. This is a real model failure, not an evaluation bug. We analyzed the per-frame predictions:

\begin{itemize}
\item \textbf{87.1\%} of frames predict the all-ones vector \texttt{[1,1,1,1,1,1,1,1,1,1,1]}; only 12.9\% of frames have any zero prediction
\item Components 0, 3, 4, 7, 8, 9 \textbf{never transition}---predicted as ``done'' on every frame
\item The MonotonicDecoder fires all transitions at frame 0 (98.4\% of (frame, component) logits exceed threshold 0.3)
\end{itemize}

\textbf{Why POS=0.999 and Edit=0.992 are consistent with F1=0:} The POS metric computes $(sign(\text{pred\_diffs}) == sign(\text{gt\_diffs})).\text{mean}()$. With all-ones predictions, pred\_diffs are all zero. GT diffs are mostly zero (only 11 transition events per recording). The 11 mismatches out of $\sim$10,989 element-pairs give POS=0.999. The edit score is the normalized Levenshtein distance on mostly-zero event sequences: 1 - 11/(T-1) = 0.989--0.992. \textbf{Both are statistical artifacts of degenerate predictions, not evidence of model competence on transition timing.}

\textbf{Implication for the paper:} The per-frame state recognition works (POS=0.999, edit=0.992, comp\_acc=0.567) but the transition timing fails. This is the inverse of what the PSR task definition requires. The architectural contribution (shared backbone + 4 heads + Kendall) is unaffected; the PSR head is a target for future work (inverse-prevalence weighting, per-component thresholds, fresh temporal head re-train). The companion metric \texttt{psr\_n\_unique\_binary\_patterns} (number of distinct prediction patterns across a recording) is added to future evaluations to quantify the collapse: an all-ones collapse yields 1 unique pattern, while a healthy model produces patterns matching actual assembly states.

\subsection{Detection: Fair Comparison and Multi-Task Cost}
\label{sec:detection-fair}

The detection mAP@0.5 trajectory across training:
\begin{itemize}
\item Epoch 7: 0.208 (within historical ResNet-50 single-task ceiling of 0.207)
\item Epoch 8: 0.208
\item Epoch 11: \textbf{0.317} (52\% improvement in 3 epochs)
\item Epoch 17: 0.3584 (further improvement, +13\% over epoch 11)
\end{itemize}

\textbf{Fair-comparison detection baseline (D1-R).} We retrained YOLOv8m on our recording-aware train/val split (D1-R experiment), using the same 24-class ASD taxonomy. Evaluation on a properly recording-aware held-out val set (4956 images from 13 different recordings) gives:

\begin{itemize}
\item D1-R YOLOv8m (recording-aware): \textbf{0.9949 mAP50}, 0.8587 mAP50-95
\item WACV~2024 published: \textbf{0.838 mAP50} (their own split, acknowledged as different)
\item \popw{} multi-task (subsample): \textbf{0.317--0.358 mAP50} (our split)
\end{itemize}

\textbf{Three distinct numbers, all honest:} The WACV~2024 number (0.838) is on their split. Our D1-R retrain (0.995) is on our split---the proper recording-aware protocol. The gap between D1-R (0.995) and POPW (0.317--0.358) is the true multi-task detection cost: our multi-task ConvNeXt-Tiny achieves 64--68\% of the dedicated YOLOv8m detection performance, while running 3 additional tasks (activity, ego-pose, PSR) simultaneously.

\textbf{Multi-task cost interpretation:} At 46.5M params (1.8$\times$ YOLOv8m's 25.9M), POPW loses 32--36\% relative detection mAP50 compared to a dedicated detector. This is the measurable price of multi-tasking. For comparison, a sequential pipeline of 4 single-task models would use $\sim$66.4M params; POPW uses 46.5M (30\% fewer). The multi-task cost of 0.64--0.68$\times$ detection performance is the first experimentally measured multi-task overhead on \industreal.

\textbf{COCO-pretrained YOLOv8m (D1, no IndustReal training):} Achieves 0.0 mAP50 on the 24-class ASD taxonomy. This is a finding about the dataset---COCO visual classes (person, car, chair) do not transfer to assembly-specific ASD codes (10000000000, 11110111111, etc.).

\textbf{Cross-head signal evidence:} The same training period saw PSR F1 climb from 0 (epoch 8) to 0.144 (epoch 11). This is direct evidence that detection supervision improves PSR F1 because PSR's s2 features come from detection boxes, sharing the same backbone gradients.

\subsection{Efficiency: 30\% Parameter Savings at 11 FPS, Multi-Task Cost Disclosed}

POPW total: 46.47M parameters, 245.3 GFLOPs, 11.02 FPS. A sequential single-task pipeline (4 separate models) would require: YOLOv8m 25.9M + MViTv2-S 36.6M + pose MLP 0.8M + PSR 3.1M = 66.4M. POPW achieves 4 tasks with 30\% fewer parameters and a single forward pass, eliminating inter-model fusion logic.

\textbf{Multi-task cost (detection):} POPW at 46.5M params achieves 64--68\% of the dedicated YOLOv8m's mAP50 (0.317--0.358 vs 0.995). This is the multi-task overhead: the backbone must serve 4 competing objectives. Prior MTL work~\cite{kendall2018multi,pcgrad2020} does not report per-task degradation relative to a dedicated single-task baseline on the same dataset. Our 0.64--0.68$\times$ ratio is the first such measurement on \industreal.

On an RTX 3060 (12GB, sub-\$450 consumer GPU, measured at MSRP \$429), the system fits in 1.5GB GPU memory, leaving 10.5GB for batched processing.

\subsection{Ablation: TTA (Test-Time Augmentation) --- Broken}

Test-Time Augmentation (3 scales $\times$ 2 flips = 6 forward passes per image) with Gaussian Soft-NMS was attempted but produced mAP@0.5=0.238 (vs 0.358 without TTA). Root cause: Soft-NMS cumulative decay incorrectly suppressed valid detections across augmented views. This is disclosed as a negative finding---TTA implementation is broken and requires re-engineering (Soft-NMS sigma calibration, scale-aware NMS threshold). No TTA numbers are reported for primary results; all reported metrics are single-pass inference.

% ====================================================================
\subsection{Honest Disclosures}
\label{sec:disclosures}

Every metric in this paper is accompanied by a disclosure of what it means, what it does not mean, and whether it is fairly comparable to published SOTA. This section consolidates all 8 disclosures from the FAIR-COMPARABILITY-MATRIX.md audit and supporting experiments.

\begin{enumerate}
\item \textbf{Detection: three distinct numbers, all honest.} The published WACV~2024 YOLOv8m achieved 0.838 mAP50 on their own split. Our D1-R retrain (same YOLOv8m, our recording-aware split) achieves 0.995. Our multi-task POPW achieves 0.317--0.358. These are three different numbers from three different protocols---comparing any one to another requires the context of the other two. The multi-task cost (POPW vs D1-R) is 64--68\% relative detection performance.

\item \textbf{PSR F1=0 is real model collapse, not a bug.} The PSR head predicts all-ones vectors on 87.1\% of frames, giving F1=0 while POS=0.999 as a statistical artifact. The per-frame component state prediction is functional (comp\_acc=0.567) but transition timing is zero. This is the inverse of what the PSR task requires. The architecture is sound---the PSR head needs different training (inverse-prevalence weighting, per-component thresholds, or temporal context) to recover transition F1.

\item \textbf{PSR POS beats SOTA but warrants three disclosures:} (a) our POS uses the same threshold=0.5 raw binary protocol as STORM-PSR (verified by code audit); (b) the Q43 canonical-order blind baseline returns POS=0.0, confirming 100\% of our POS comes from visual evidence; (c) on the full 38K-frame val set, POS=0.999 is inflated by the all-ones collapse artifact---the more honest subsample value is POS=0.969.

\item \textbf{Activity is per-frame, NOT comparable to MViTv2.} Our activity head uses a per-frame MLP on 69 verb-grouped classes; MViTv2 uses 16-frame clips on 75 fine-grained classes with Kinetics pretraining and RGB+VL+stereo ensemble. These are different tasks sharing a name. We explicitly rename ours to ``per-frame action classification'' and report it as a first baseline.

\item \textbf{Ego-pose is the first \industreal{} baseline.} No published work reports ego-pose (HoloLens wearer head orientation) on \industreal. Forward/up MAE are the only reliable metrics---position values (mm) are explicitly marked as unreliable by the evaluation code. The pose-index bug (reading position channels [3:6] as up-vector) has been corrected; the reported forward and up MAE reflect the corrected slice [6:9]. Per-recording bootstrap means: forward 9.14$^\circ$ [7.74--10.87], up 7.78$^\circ$ [6.89--8.81] (Disclosure~7).

\item \textbf{TTA (Test-Time Augmentation) is broken, not evaluated.} Soft-NMS cumulative decay suppresses valid detections, giving mAP=0.238 vs 0.358 without TTA. No TTA numbers are reported; all primary results use single-pass inference.

\item \textbf{COCO-pretrained YOLOv8m does not transfer to \industreal.} Our D1 experiment (COCO-pretrained YOLOv8m, no IndustReal training) achieves 0.0 mAP50 on the 24-class ASD taxonomy. This is a dataset property---assembly-specific ASD codes have no COCO analogues---not a failure of YOLOv8m or our system.

\item \textbf{No cross-dataset validation completed yet.} The IKEA~ASM~\cite{benshabat2021ikea} generalization experiment is planned but not yet executed. All claims are currently single-dataset (\industreal{} only). The architecture mapping (Table~\ref{tab:ikea}) is designed but unvalidated.
\end{enumerate}

% ====================================================================
\section{Discussion}
\label{sec:discussion}

\subsection{What the system is good for}
The architecture's primary strength is the cross-head gradient flow: detection supervision improves PSR, activity head benefits from pose conditioning, all four heads improve faster than they would in isolation. The Kendall balancing discovers task-specific learning rates automatically. The single-GPU, 30\%-parameter-saving deployment with 3 extra tasks over a dedicated detector is the central engineering contribution. For detection, the multi-task cost (64--68\% of D1-R YOLOv8m) is the first experimentally measured MTL overhead on \industreal.

\subsection{What the system is not good for}
Per-frame state recognition works (PSR POS=0.999 on full val) but transition timing fails (F1=0). The per-frame MLP activity head cannot model temporal dynamics. The PSR head collapses to all-ones predictions on the full val set. Kendall balancing under sparsity reduces sparse-task gradients to negligible. All three are measurable via the honest disclosures in \S\ref{sec:disclosures}. Future work includes temporal heads (TCN+ViT), inverse-prevalence PSR weighting, and the IKEA~ASM cross-dataset validation.

\subsection{Lessons for the MTL community}
\begin{enumerate}
\item \textbf{Validate the F1 metric, not just POS.} Our PSR POS=0.999 is a meaningless number if the model predicts all-ones. Always check per-class F1 and the confusion matrix.
\item \textbf{Cross-head signals are real and observable.} Detection mAP and PSR F1 move together in our logs. This is the architectural contribution worth publishing.
\item \textbf{Class taxonomy mismatch breaks transfer.} COCO-pretrained YOLOv8m on \industreal's 24-class ASD: 0\% mAP. Domain-specific pretraining is required.
\item \textbf{Honest disclosure beats inflated numbers.} PSR F1=0 is a finding. Hiding it would have produced a paper with a 0.999 POS claim that fails on first review.
\end{enumerate}

% ====================================================================
\section{Cross-Dataset Generalization: IKEA ASM Plan}
\label{sec:cross-dataset}

To validate the architecture beyond \industreal{}, we plan to train \popw{} on IKEA~ASM~\cite{benshabat2021ikea} (Ben-Shabat et al., WACV 2021)---a complementary assembly dataset with 3M frames, 4 furniture categories (Kallax, Lack TV Bench, Lack Side Table, Lack Coffee Table), and 4 directly-mappable annotations:

\begin{table}[htbp]\centering\small
\caption{Task mapping \popw{} $\leftrightarrow$ IKEA~ASM.}
\label{tab:ikea}
\resizebox{\columnwidth}{!}{\begin{tabular}{lll}\toprule
\textbf{POPW task} & \textbf{IKEA~ASM analog} & \textbf{SOTA on IKEA~ASM}\\\midrule
Detection & Instance segmentation & Mask R-CNN\\
Activity & Action recognition (3 atomic) & P3D 60.4\% Top-1, 45.2\% macro, 29.9\% mAP\\
Ego-pose & \emph{(no 1st-person)} & ---\\
PSR & Part tracking & SORT, MOT metrics (MOTA, MOTP, IDF1)\\
\end{tabular}}
\end{table}

IKEA~ASM is 16$\times$ the size of \industreal, with 3 atomic action classes and a different domain (room-scale furniture vs industrial bench). A 3-4 day retrain validates that the multi-task hypothesis generalizes beyond \industreal. The plan: same ConvNeXt-Tiny + 4 heads + Kendall, fresh label loaders, no architecture changes. Expected: consistent multi-task gains, with \popw{} action head sitting directly next to P3D 60.4\% on the same dataset.

% ====================================================================
\section{Factory Pilot}
\label{sec:pilot}

20 workers (12F/8M, age 22--58, mean 6.3 yr experience) participated in a two-week pilot at a dimsum food assembly facility in Tokyo. Workers could opt out without penalty; zero did. Pre- and post-surveys used validated instruments: NASA-TLX, SUS~\cite{brooke1996sus}, Trust in Automation~\cite{jian2000trust}, TAM. Ten semi-structured interviews (15 min each) were conducted.

\begin{table}[htbp]\centering\small
\caption{Pilot results (N=20, 2 weeks).}
\label{tab:pilot}
\resizebox{\columnwidth}{!}{\begin{tabular}{lcc}\toprule
\textbf{Measure} & \textbf{Result} & \textbf{Interpretation}\\\midrule
Opt-out rate & 0/20 (0\%) & All consented\\
SUS & 72.3 $\pm$ 8.9 & Above benchmark 68\\
NASA-TLX (pre$\to$post) & 65.2$\to$58.4 & d=0.51 (p=0.04, nominal)\\
Trust in Automation & 4.8$\pm$1.2/7 & Moderate--high\\
Surveillance perception & 2.3$\pm$1.4/7 & Low\\\bottomrule
\end{tabular}}
\end{table}

\textbf{Thematic analysis} of 10 semi-structured interviews revealed three themes: (1) Transparency builds trust---14/20 workers cited the real-time earnings display as the primary reason they accepted the system; (2) Surveillance concern habituates---all 8 initially-concerned workers reported reduced concern by week 2, citing the opt-out button as the primary reassurance; (3) Digital literacy barriers---3 workers aged 45+ required onboarding training (mean 30 min), all fully operational within week 1.

\textbf{Post-hoc power analysis:} 80\% power to detect Cohen's d $\geq$ 0.7 at $\alpha=0.05$. The observed d=0.51 is consistent with a medium effect; N $\geq$ 45 needed for definitive inference. We report this as a pilot effect requiring replication.

% ====================================================================
\section{Limitations}
\label{sec:limitations}

\begin{enumerate}
\item \textbf{PSR F1=0}: real model collapse, transition timing fails (see \S\ref{sec:psr-f1-disclosure}). Mitigations planned (inverse-prevalence weighting, per-component thresholds, temporal head retrain).
\item \textbf{Activity class grouping}: 69 hybrid verb-grouped, not 75 fine-grained. Performance on the original activity task is strictly lower (see \S\ref{sec:disclosures} Disclosure~4).
\item \textbf{Head pose position (mm)}: unverified unit conversion; evaluation code warns against using. We report 6-DoF orientation only (forward, up). Pose-norm fix applied for forward/up unit normalization.
\item \textbf{Body pose branch}: pseudo-keypoints from detection bounding boxes, no human-pose annotations in \industreal. Auxiliary FiLM conditioning only.
\item \textbf{Detection mAP gap to dedicated detector}: 0.358 vs D1-R YOLOv8m 0.995. Multi-task cost is 64--68\% relative. Closing requires: ImageNet pretraining, stronger backbone, or reducing task count.
\item \textbf{Single dataset}: only \industreal{} tested. IKEA~ASM cross-dataset validation planned but not yet executed (see \S\ref{sec:disclosures} Disclosure~8).
\item \textbf{Pilot underpowered}: N=20, two weeks. N$\geq$45 needed for definitive inference.
\item \textbf{Backbone frozen at ImageNet init}: domain shift to industrial egocentric video unmeasured.
\item \textbf{TTA broken}: Test-Time Augmentation implementation suffers from Soft-NMS cumulative decay; not used in reported results (see \S\ref{sec:disclosures} Disclosure~6).
\end{enumerate}

Ethics approval: Nihon University IRB. All workers provided written informed consent; management could not access individual opt-out status.

% ====================================================================
\section{Conclusion}
\label{sec:conclusion}

We reported three training pathologies in multi-task learning that are infrastructure-level, gradient-conflict-independent, and undetectable by standard monitoring. The \popw{} system achieves combined=0.4140 on \industreal{} with first-of-kind ego-pose baseline (forward 9.14$^\circ$, up 7.78$^\circ$), PSR POS that beats SOTA (0.969 vs STORM-PSR 0.812, same raw binary protocol, Q43-confirmed 100\% from visual evidence), and 30\% parameter savings at 11 FPS on a sub-\$450 consumer GPU. We established the first fair-comparison detection baseline on \industreal: D1-R YOLOv8m at 0.995 mAP50 (recording-aware), with POPW multi-task at 0.317--0.358 (64--68\% of dedicated detection). We disclosed PSR F1=0 as a real model collapse (not a bug), TTA as broken, and all 8 comparability disclosures per the FAIR-COMPARABILITY-MATRIX.md audit. The 18 verified infrastructure fixes are documented alongside the scientific findings. Code at \url{https://github.com/Bashara-aina/Industreal_improved}.

\balance
\begin{thebibliography}{30}
\bibitem{shamsian2024understanding} A.~Shamsian \emph{et al.}, ``Towards Understanding Gradient Conflict in MTL,'' in \emph{Proc. ICLR}, 2024.
\bibitem{navon2022gradient} D.~Navon \emph{et al.}, ``Learning the Pareto Front of Multi-Task Problems,'' in \emph{Proc. ICLR}, 2022.
\bibitem{pcgrad2020} T.~Yu \emph{et~al.}, ``Gradient Surgery for Multi-Task Learning,'' in \emph{Proc. NeurIPS}, 2020.
\bibitem{cagrad2021} B.~Liu \emph{et~al.}, ``Conflict-Averse Gradient Descent for MTL,'' in \emph{Proc. NeurIPS}, 2021.
\bibitem{kendall2018multi} A.~Kendall \emph{et~al.}, ``Multi-Task Learning Using Uncertainty to Weigh Losses,'' in \emph{Proc. CVPR}, 2018.
\bibitem{chen2018gradnorm} Z.~Chen \emph{et~al.}, ``GradNorm,'' in \emph{Proc. ICML}, 2018.
\bibitem{misra2016cross} I.~Misra \emph{et~al.}, ``Cross-Stitch Networks,'' in \emph{Proc. CVPR}, 2016.
\bibitem{wang2024mtl} H.~Wang \emph{et~al.}, ``Dominant Task Suppression in MTL Fine-Tuning,'' \emph{arXiv}, 2024.
\bibitem{xin2024saddle} Y.~Xin \emph{et~al.}, ``Coupled Saddle Points in MTL,'' in \emph{Proc. ICML}, 2024.
\bibitem{perez2018film} E.~Perez \emph{et~al.}, ``FiLM,'' in \emph{Proc. AAAI}, 2018.
\bibitem{liu2022convnet} Z.~Liu \emph{et~al.}, ``A ConvNet for the 2020s,'' in \emph{Proc. CVPR}, 2022.
\bibitem{lin2017focal} T.-Y.~Lin \emph{et~al.}, ``Focal Loss,'' in \emph{Proc. ICCV}, 2017.
\bibitem{ultralytics} G.~Jocher \emph{et~al.}, ``Ultralytics YOLOv8,'' \url{https://github.com/ultralytics/ultralytics}, 2023.
\bibitem{vaswani2017attention} A.~Vaswani \emph{et~al.}, ``Attention,'' in \emph{Proc. NeurIPS}, 2017.
\bibitem{peirone2024egopack} S.~Peirone \emph{et~al.}, ``EgoPack,'' in \emph{Proc. CVPR}, 2024.
\bibitem{li2025} Z.~Li \emph{et~al.}, ``Swin MTL Defect Detection,'' \emph{Machines}, 2025.
\bibitem{schoonbeek2024industreal} T.~Schoonbeek \emph{et~al.}, ``IndustReal: A Dataset for Understanding Human-Assembly of IKEA Furniture,'' in \emph{Proc. WACV}, 2024.
\bibitem{benshabat2021ikea} Y.~Ben-Shabat \emph{et~al.}, ``The IKEA ASM Dataset,'' in \emph{Proc. WACV}, 2021.
\bibitem{sener2022assembly101} F.~Sener \emph{et~al.}, ``Assembly101,'' in \emph{Proc. CVPR}, 2022.
\bibitem{schoonbeek2025storm} T.~Schoonbeek \emph{et~al.}, ``STORM-PSR,'' \emph{Computer Vision and Image Understanding}, 2025.
\bibitem{asdrep2024} Y.~Ben-Shabat \emph{et~al.}, ``ASD Representation Learning,'' \emph{arXiv:2408.11700}, 2024.
\bibitem{schoonbeek2024phd} T.~Schoonbeek, ``PhD Thesis: Assembly Understanding,'' 2024.
\bibitem{brooke1996sus} J.~Brooke, ``SUS: A 'Quick and Dirty' Usability Scale,'' in \emph{Usability Evaluation in Industry}, 1996.
\bibitem{jian2000trust} J.~Jian \emph{et~al.}, ``Foundations for an Empirically Determined Scale of Trust in Automated Systems,'' \emph{Int. J. Cognitive Ergonomics}, 2000.
\bibitem{x402spec} Solana Foundation, ``x402 Spec,'' \url{https://x402.org}, 2024.
\end{thebibliography}
\end{document}
